The Blessing of FedAvg's Linear Speedup in Federated Learning

### 2020-06-01 source/sec_exp.tex
exp and sec 6 add threm id

% ~\ref{th:strongcvxsmth}~\ref{th:cvxsmoth}~\ref{th:fedmasslr}
\textbf{Linear speedup.} To verify the linear speedup results in Theorems
\lkxcom{cite sgd theorems}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $\vw_0 = \textbf{0}_d$ and measure. For each configuration, we run three random seeds and report
the best seed results for each configuration $(E, K)$. In each configure, we
extensive search the stepsize from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^i \ \forall i \in \ZZ$. As the results shown in Figure~\ref{fig:speedup} (1st row),
the number of iterations to reach the target accuracy $\epsilon$ decreasing 
as the number of workers increase.

@@

\textbf{Nesterov accelerated FedAvg.} In the third row of Figure~\ref{fig:speedup}, 
we report the last iteration to converge to $\epsilon$-accuracy of Nesterov accelerated FedAvg. The empirical observations align with our theorems \lkxcom{cite accelerated theorems} that the accelerated version of FedAvg can also achieve the linear speedup
w.r.t the number of workers.

>>>>

% ~\ref{th:strongcvxsmth}~\ref{th:cvxsmoth}~\ref{th:fedmasslr}
\textbf{Linear speedup.} To verify the linear speedup results of FedAvg in Theorem~\ref{thm:SGD_scvx}~\ref{thm:SGD_cvx}, we evaluate the number of iterations needed to reach
$\epsilon$-accuracy in three objectives. We initialize all runs with $\vw_0 = \textbf{0}_d$ and measure. For each configuration, we run three random seeds and report
the best seed results for each configuration $(E, K)$. In each configure, we
extensive search the stepsize from $\min(\eta_0, \frac{nc}{1 + t})$, where
$\eta_0 \in \{0.1, 0.12, 1, 32 \}$ according to different problems and $c$ can
take the values $c = 2^i \ \forall i \in \ZZ$. As the results shown in Figure~\ref{fig:speedup} (1st row),
the number of iterations to reach the target accuracy $\epsilon$ decreasing 
as the number of workers increase.

@@

\textbf{Nesterov accelerated FedAvg.} In the third row of Figure~\ref{fig:speedup}, 
we report the last iteration to converge to $\epsilon$-accuracy of Nesterov accelerated FedAvg. The empirical observations align with Theorem~\ref{thm:nesterov_scvx}~\ref{thm:Nesterov_cvx} that the accelerated version of FedAvg can also achieve the linear speedup
w.r.t the number of workers.
